\documentclass{resume}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \usepackage{fontawesome}
\usepackage{fontawesome5}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=blue
}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\name{\;\;\;\;\;\;\;\;\;\;\;Ilya Drobyshevskiy} % Your name
\address{Moscow, Russia} % Your address
\address{
    \faTelegram \enspace \href{https://t.me/free001style}{free001style}\\
    \faGithub \enspace \href{https://github.com/free001style}{free001style}\\
    \faEnvelope \enspace \href{mailto:iadrobyshevskiy@edu.hse.ru}{iadrobyshevskiy@edu.hse.ru}
}   


\begin{document}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Higher School of Economics}{Moscow, Russia}
      {Bachelor of Applied Mathematics and Computer Science;  GPA: 6.44}{Sep 2021 -- Present}
      \resumeItemListStart
      \medskip
      \resumeItem{Relevant courses} {Algorithms and Data Structures, Programming in Python, C++, Linear Algebra, Probability Theory and Statistics, Graph Theory, Abstract Algebra, Calculus.}
      \resumeItemListEnd
      \bigskip
      \resumeSubheading
        {Olphys school(physics)}{Moscow, Russia}{}{Oct 2019 -- Nov 2019}
        \bigskip
      \resumeSubheading
        {Olphys school(physics)}{Moscow, Russia}{}{Oct 2017 -- Nov 2017}
        \bigskip
      \resumeSubheading
        {Gymnasium №7}{Vitebsk, Belarus}{GPA: 9.5}{Sep 2010 -- May 2021}
  \resumeSubHeadingListEnd

\section{Skills}
 \resumeSubHeadingListStart
    \item{
    \textbf{Languages}{: Russian (Native), English (Upper-Intermediate), Polish (Upper-Intermediate)}
    }
    \smallskip
   \item{
     \textbf{Programming languages}{: Python, C/C++, Bash, Assembly}
   }
   \smallskip
   \item{\textbf{Technologies}{: Git, Docker, GDB, SQL, Markdown, HTML}}
   \smallskip
   \item{\textbf{Software skills}{: Django, Flask, NumPy, Pandas, Plotly/Dash}}
 \resumeSubHeadingListEnd


\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/free001style/Cian_Avito_project}{Cian-Avito}}
      {A team Python/Vue.js project, the essence of which is to obtain information about apartments from popular services and display on the map with option immediately calculate the mortgage (number of years, monthly payment).}
      \bigskip
    \resumeSubItem{\href{https://github.com/free001style/image_processor}{Image-processor}}
      {A console application that allows to apply various filters to images, similar to filters in popular graphic editors.}
      \bigskip
     \resumeSubItem{\href{https://github.com/free001style/Deep_Python-HSE/blob/main/HW-1_data_analysis/Drobyshevskiy_Ilya_HW_1_data_analysis.ipynb}{Olist analyzing}}
      {In this notebook I tried myself as an analyst in the Brazilian marketplace Olist. I researched the data and made conclusions based on them that will help the business grow.}
      \bigskip
    \resumeSubItem{\href{https://github.com/free001style/LinearAlgebra-HSE/blob/main/homework-practice-02-linregr-Drobyshevskiy.ipynb}{Diamond price prediction}}
      {Linear model for diamond price prediction. Used optimizations: polynomial features, L2-regularization.}
      \bigskip
    \resumeSubItem{\href{https://github.com/free001style/LinearAlgebra-HSE/blob/main/homework_practice_03_linregr.ipynb}{SVD}}
      {Example of data compression with singular value decomposition.}
    
  \resumeSubHeadingListEnd


\section{Teaching Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Higher School of Economics}{Moscow, Russia}
      {Teacher assistant on the Linear Algebra course}{Sep 2022 -- Present}
      \resumeItemListStart
      \medskip
      \resumeItem{Tasks} {Checking individual homeworks of a group of 30 people, assistance in conducting exams and consultations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd




\section{Experience}
Nothing so far, but I'm doing my best

\end{document}